---
title: "Five Decades of Global Terrorism"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    css: styles.css
    social: [ "twitter"]
    source_code: embed
---


```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(hrbrthemes)
library(ggsci)

df <- read_csv("global_terror_clean.csv") 

theme_terr <- function() { 
  theme_modern_rc(plot_title_size = 30) %+replace% 
    theme(
      plot.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      legend.position = "none",
      axis.text.x = element_text(size = 18),
      axis.text.y = element_text(size = 18,hjust=1)
    )
}

theme_set(theme_terr())
```

Data source: National Consortium for the Study of Terrorism and Responses to Terrorism (START). (2018). Global Terrorism Database [Data file].<br>Retrieved from https://www.start.umd.edu/gtd

Overview 
=======================================================================

Row
-----------------------------------------------------------------------

### Number of attacks { .colored_smallbox}

```{r}
n_attacks <- nrow(df)
n_attacks <- format(n_attacks,big.mark   = ",")
valueBox(n_attacks, icon = "fa-fire")
```

### Number of casualties { .colored_smallbox }

```{r}
n_kills <- sum(df$nkill,na.rm=T)
n_kills <- format(n_kills,big.mark   = ",")
valueBox(n_kills, icon = "ion-man")
```

### % Succesful attacks { .colored }

```{r}
pct <- round(nrow(df[df$success==1,]) / nrow(df) *100,2)
gauge(pct, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(0, 1.0), warning = c(1.1, 2), danger = c(2.1, 100),
  colors = "darkred"
))
```

Row
-----------------------------------------------------------------------

### Number of attacks by year { .colored }

```{r}
df %>%
  group_by(year) %>%
  count() %>%
  ggplot(aes(year,n)) +
  geom_line(colour="darkred", size = 1) +
  scale_y_continuous(labels = function(n) {
    trans = n / 1000
    paste0(trans, "K")
  })
```

### Number of kills by year { .colored }

```{r}
df %>%
  group_by(year) %>%
  summarise(n = sum(nkill,na.rm=T)) %>%
  ggplot(aes(year,n)) +
  geom_line(colour="darkred", size = 1) +
  scale_y_continuous(labels = function(n) {
    trans = n / 1000
    paste0(trans, "K")
  })
```

Attack info 
=======================================================================

Row
-----

### Most used weapons { .colored}

```{r}
df %>%
  mutate(weaptype1_txt = recode(weaptype1_txt,"Vehicle (not to include vehicle-borne explosives, i.e., car or truck bombs)" 
="Vehicle")) %>%
  group_by(weaptype1_txt) %>%
  count() %>%
  arrange(desc(n)) %>%
  ungroup() %>%
  top_n(10) %>%
  mutate(pct = n/sum(n)*100) %>%
  ggplot(aes(reorder(weaptype1_txt,pct),pct, fill = pct)) +
  geom_col(colour=NA) +
  scale_fill_material("red") +
  scale_y_percent(scale=1) +
  coord_flip()
```

### Most common attack types { .colored}

```{r}
df %>%
  group_by(attacktype1_txt) %>%
  count() %>%
  ungroup() %>%
  top_n(10) %>%
  mutate(attacktype1_txt = recode(attacktype1_txt, 
        "Facility/Infrastructure Attack" = "Facility/Infrastr.", 
        "Hostage Taking (Barricade Incident)" = "Hostage Taking",
        "Hostage Taking (Kidnapping)" = "Kidnapping"),
         pct = n/sum(n)*100) %>%
  ggplot(aes(reorder(attacktype1_txt,pct),pct, fill = pct)) +
  geom_col(colour=NA) +
  scale_fill_material("red") +
  scale_y_percent(scale=1) +
  coord_flip()
```

### Most common targets {.colored}

```{r}
df %>%
  filter(!is.na(target1)) %>%
  group_by(target1) %>%
  count() %>%
  arrange(desc(n)) %>%
  ungroup() %>%
  top_n(10) %>%
  mutate(pct = n/sum(n)*100) %>%
  ggplot(aes(reorder(target1,pct),pct, fill = log(pct))) +
  geom_col(colour=NA) +
  scale_fill_material("red") +
  scale_y_percent(scale=1) +
  coord_flip()
```

Row
---
### Attacks in history with the most casualties  {.colored}
```{r fig.width=15, fig.height=7}
df %>%
  mutate(id = paste(year,city,country_txt,"-",attacktype1_txt)) %>%
  select(date,id,nkill,nwound) %>%
  distinct(id, .keep_all = T) %>%
  arrange(desc(nkill)) %>%
  top_n(15,nkill) %>%
  ggplot(aes(x = reorder(id,nkill),y=nkill,fill=log(nkill))) +
  geom_col(colour=NA) +
  coord_flip() +
  scale_fill_material("red")
```

Interactive map 
=======================================================================

Shiny slider, n attack and n kills by country

Animated map 
=======================================================================

Row {.tabset .tabset-fade}
---

### Global attacks through time { .colored}
```{r fig.height=15, fig.width=18}

library(maps)
library(ggthemes)
library(gganimate)

df <- read_csv("global_terror_clean.csv")

df <- df %>% filter(nkill>0)

world <- ggplot() +
  borders("world", colour = "gray85", fill = "gray80") +
  theme_map() +
  theme(plot.background = element_rect(fill="#2B2828"),
        plot.title = element_text(size= 18,colour="snow"),
        legend.position = "none") +
  coord_map(xlim=c(-180,180)) +
  scale_y_continuous(limits=c(-60,90)) +
  theme(panel.background = element_blank())

map2 <- world +
  #geom_point(aes(x = longitude, y = latitude, size = nkill),
  #           data=df,colour = 'darkred', alpha = .2) +
  geom_point(aes(longitude, latitude,size=nkill), color = "darkred",
             alpha=.5, data=df) + 
  scale_size_continuous(range = c(2, 12)) +
  # transition_states(year,
  #                   transition_length = 2,
  #                   state_length = 1) +
  # ggtitle('Year: {closest_state}')
  transition_time(year) +
  labs(title = "Year: {round(frame_time,0)}")

animate(map2,fps=3,nframes=n_distinct(df$year),width = 900, height = 600,
        bg = 'transparent')

```

### Attacks by region { .colored}

```{r fig.width = 18, fig.height=15}

regions <- df %>%
  group_by(year,region_txt) %>%
  count() %>%
  ungroup() %>%
  complete(year,region_txt,fill=list(n=0)) %>%
  group_by(region_txt) %>%
  mutate(cs = cumsum(n)) %>% 
  ungroup() %>%
  group_by(year) %>%
  arrange(year,desc(cs)) %>%
  mutate(order = rev(row_number())) %>%
  mutate(Rank = rank(-cs),
         Value_rel = cs/cs[Rank==1],
         Value_lbl = paste0(" ",round(cs/1e9)))  %>%
  ungroup() 

p<-regions %>%
  ggplot(aes(order,Value_rel,fill=region_txt,group=cs)) +
  #geom_col(colour=NA) +
  geom_tile(aes(y=cs/2,height=cs),width=0.9,show.legend = F)+
  coord_flip(clip="off") +
  scale_fill_viridis_d() +
  transition_states(year, transition_length = 4, state_length = 1) +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(1,1,1,6, "cm")) +
    labs(title = "Year: {closest_state}") +
  geom_text(aes(y = 0, label = paste(region_txt, " ")), vjust = 0.2, hjust = 1,colour="snow") 

#animate(p,fps=2.5,nframes = n_distinct(regions$year)*2)
animate(p, 100, fps = 25, duration = 15.6, width = 1000, height = 600)

```